---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)

```

# Introduction




# Data


```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path

data<- load(here::here("inputs/data/deepfake.RData"))

EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Sanders,believed_true)

EDA<-na.omit(EDA) #remove NA

```


## EDA

### treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
EDA<-EDA%>%
  drop_na(treat)

treat_map <- 
  EDA%>%
  ggplot(aes(x = treat, fill = treat)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  labs(title = "Treat distribution",x="", y="Count") +
  theme_minimal()

treat_map

```


### education level distribution by PID 
```{r educationPID, fig.cap = "Educational level by PID",echo=FALSE, fig.width=10, fig.height=7}
edu <- 
  EDA%>%
  ggplot(aes(x = educ,fill=PID, )) +
  geom_bar(position="dodge") +
  labs(title = "Citizens with a high school degree or above are more likely to suppprt democratic and republican party",x= "Educational Level", y="Count")+
  scale_fill_manual(name = "Political Parties",values = c("#DB7558", "#FFCF57","#8FCDD4"))

edu
```






### sexim by education level 
```{r sexim, fig.cap = "sexim by education level",echo=FALSE, fig.width=5, fig.height=4}
EDA<-EDA%>%
  drop_na(ambivalent_sexism)

s1<-
  ggplot(EDA, aes(x = PID, y= ambivalent_sexism)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="sexim by education level", x="PID", y="Sexism")+
  theme_economist() + scale_fill_economist()
s1
```


<<<<<<< HEAD
## internet usage frequency by education level
```{r internet, fig.cap = "internet usages",echo=FALSE, fig.width=15, fig.height=5}

G1<-ggplot(EDA, aes(x=internet_usage, fill=EDA$educ)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by education level ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))

G2<-ggplot(EDA, aes(x=internet_usage, fill=EDA$meta_OS)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by devices ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))


G3<-ggplot(EDA, aes(x=internet_usage, fill=EDA$age_65)) + 
    geom_area(alpha=0.8 , size=0.2, colour="black", stat = "count")+
    labs(title = "Internet usage frequency by age group ",y="Counts",x="Days")+
    scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6"))


# combine two diagram in one graph
ggarrange(
  G1, G2, G3, 
  ncol = 3, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```



### post favor by treat
```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Sanders)

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()


```

### Average deception level by treat
```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")
```


  


# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

## Second discussion point

## Third discussion point

## Weaknesses and next steps



\newpage

\appendix

# Appendix





\newpage


# References


